The Effects of weather on maize yield: New evidence from Kenya

### 2018-12-26 writing/draft3/draft19.tex
(re)writing

\begin{threeparttable}
\singlespacing
\caption{Alternative to adjusted R2}\label{R2}
\begin{tabular}{@{}lll}
\\[-1em]
\br
\\[-1em]
&\multicolumn{2}{c}{\textbf{County level dummy variables:}}\\
\textbf{Sample:}&Yes&No\\
\textbf{All counties}& $0.507$&$0.307$\\
\textbf{ASAL}& $0.379$&$0.170$\\
\textbf{non-ASAL}&  $0.501$&$0.307$\\
\br
\end{tabular}

\end{threeparttable}

>>>>

\begin{center}
\begin{threeparttable}
\caption{\label{R2}Coefficient of determination $R^2$ for mixed models}
\begin{indented}
\item[]
\begin{tabular}{@{}lcc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&Marginal\tnote{a}&Conditional\tnote{b}\\
\hline
{All counties}& $0.300$&$0.526$\\
{ASAL}& $0.134$&$0.353$\\
{non-ASAL}&  $0.153$&$0.436$\\
\br
\end{tabular}
\begin{tablenotes}
\begin{footnotesize}
    \item \textit{Notes:} The coefficient of determination from generalised linear mixed-effects models. The statistic is based on \cite{Nakagawa2013}.  \\
        \begin{adjustwidth}{1cm}{}
    \item[a] The marginal coefficient is interpreted as the variance explained by the fixed effects
  \item[b] while the conditional one is explained by both fixed affects and random effects (in our case by fixed effects and random intercepts
     \end{adjustwidth}
     \end{footnotesize}
\end{tablenotes}

\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}
